Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-17 paper_jasa.tex
double spacing makes page size = 45
author email added

% \usepackage{pifont} % this package is used to print check mark \checkmark

@@

% Article top matter
\title{Validation of Visual Statistical Inference, Applied to Linear Models}
\author{
{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
\thanks{Mahbubul Majumder is Graduate Student, Heike Hofmann is Associate  Professor, Dianne Cook is Full Professor, Department of
Statistics and Statistical Laboratory, Iowa State University,
Ames, IA 50011-1210. This research is supported in part by the
National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.7in}}
%\date{\today}  %\today is replaced with the current date
\maketitle

>>>>

% \usepackage{pifont} % this package is used to print check mark \checkmark
%\linespread{2}

@@

% Article top matter
\title{Validation of Visual Statistical Inference, Applied to Linear Models}
\author{
{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
\thanks{Mahbubul Majumder is Graduate Student (e-mail: mahbub72@gmail.com) , Heike Hofmann is Associate  Professor and Dianne Cook is Full Professor, Department of
Statistics and Statistical Laboratory, Iowa State University,
Ames, IA 50011-1210. This research is supported in part by the
National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.7in}}
%\date{\today}  %\today is replaced with the current date
\maketitle
